Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-08 bckground.tex
pending minor fix.
Addendum to Related Work.

AliEn, DIRAC, GlideinWMS and PanDA also have similar implementations. These
WMS were initially implemented to use Grid resources using the Condor software
ecosystem~\cite{thain2005distributed}. Accordingly, all LHC WMS implemented
Grid-like authentication and authorization systems and adopted a computational
model based on distributing a large amount of single/few-cores tasks across
hundreds of sites\mtnote{Is this true?}.

All LHC experiments produce and process large amounts  of data from actual
collisions in the accelerator and from their simulations. Dedicated, multi-
tiered data systems have been built to store, replicate, and distributed these
data. All LHC WMS interface with these systems to move data to the sites where
related compute tasks are executed or to schedule compute tasks where (large
amount of) data are already stored.

>>>>

AliEn, DIRAC, GlideinWMS and PanDA also have similar implementations. These
WMS were initially implemented to use Grid resources using the Condor software
ecosystem~\cite{thain2005distributed}. Accordingly, all LHC WMS implemented
Grid-like authentication and authorization systems and adopted a computational
model based on distributing a large amount of single/few-cores tasks across
hundreds of sites.

All LHC experiments produce and process large amounts  of data from actual
collisions in the accelerator and from their simulations. Dedicated,  
multi-tiered data systems have been built to store, replicate, and distributed these
data. All LHC WMS interface with these systems to move data to the sites where
related compute tasks are executed or to schedule compute tasks where (large
amount of) data are already stored.

It is interesting to note that most WMS developed to support LHC experiments are gradually evolving towards HPC resources, though none have reached sustained operational usage at the scales that PanDA has achieved for ATLAS on Titan.
